### 2015-06-26 design.tex
Learned or hand-mode domains? --- over to RPG

In all of these experiments, we define sensor arrangements, and probabilities for attacks, confounding
benign events, and sensor false positives and false negatives. We sample from
them to find ground truth and sensor report sets, run MIFD on the sensor
reports, and evaluate its accuracy.
These experiments are necessarily artificial, since they assume
omniscience about parameters which are even in principle inaccessible.

@@

% DONE: Can you give the reader a sense of the distinction between
% configuration, setting, and run? The notion of "run" is relatively clear, but
% not the other two.  Something like "For example, a configuration might specify
% how a set of attacks is generated, and the set of sensors. A particular
% setting would involve a particular set of possible attacks, a particular set
% of sensors, and a particular set of sensing relations between attacks and
% sensors."
%
% FIXME - Robert, in the marked-up PDF you suggested discussing
% locations, but earlier we'd decided to prune that discussion, since
% we didn't end up using different locations.
% Right, but here how will the reader know that we are going to sample from the
% same event multiple times?  The fact is that the whole notion of "run" as
% distinct from "location" is broken, so we must make the best of it that we
% can.  Please have a whack at this.
For each experiment we create a \emph{configuration},
a set of parameters specifying how a set of events and sensors, a
\emph{setting}, is generated.  A
setting comprises a set of possible attacks, a set
of sensors, and a set of sensing relations between attacks and
sensors.
In each \emph{run} of a setting we sample %, for each location,
% some number of 
from the attack and benign events.
% These are
% Bernoulli random variables; we discuss setting their probabilities
% below.
In each experiment, for each configuration, we generated 1,000 settings
and conducted 100 runs per setting.
%
After sampling events, we sample from the sensors
%at the corresponding location,
according to their false positive and false negative probabilities.  
\hide{For each of
the $i$ events which the sensor might detect, we consider the probability
$\mathit{fn}$ of a false negative, so the probability of the sensor firing is $1
- \mathit{fn}^i$. If none of the sensed events occurred, the sensor will fire
according to its false positive probability.
}

>>>>

In all of these experiments, we define sensor arrangements as well as the probabilities for attacks, confounding
benign events, sensor false positives and false negatives. We sample from
them to find ground truth and sensor report sets, run MIFD on the sensor
reports, and evaluate its accuracy.
These experiments are necessarily artificial, since they assume
omniscience about parameters which are even in principle inaccessible.

@@

% DONE: Can you give the reader a sense of the distinction between
% configuration, setting, and run? The notion of "run" is relatively clear, but
% not the other two.  Something like "For example, a configuration might specify
% how a set of attacks is generated, and the set of sensors. A particular
% setting would involve a particular set of possible attacks, a particular set
% of sensors, and a particular set of sensing relations between attacks and
% sensors."
%
% FIXME - Robert, in the marked-up PDF you suggested discussing
% locations, but earlier we'd decided to prune that discussion, since
% we didn't end up using different locations.
% Right, but here how will the reader know that we are going to sample from the
% same event multiple times?  The fact is that the whole notion of "run" as
% distinct from "location" is broken, so we must make the best of it that we
% can.  Please have a whack at this.
For each experiment we create a \emph{configuration},
a set of parameters specifying how a set of events and sensors, a
\emph{setting}, is generated by sampling random variables and
comparing to these parameters.  A
setting comprises a set of possible attacks, a set
of sensors, and a set of sensing relations between attacks and
sensors.
In each \emph{run} of a setting we sample %, for each location,
% some number of 
from the attack and benign events.
% These are
% Bernoulli random variables; we discuss setting their probabilities
% below.
In each experiment, for each configuration, we generated 1,000 settings
and conducted 100 runs per setting.
%
After sampling events, we sample from the sensors
%at the corresponding location,
according to their false positive and false negative probabilities.  
\hide{For each of
the $i$ events which the sensor might detect, we consider the probability
$\mathit{fn}$ of a false negative, so the probability of the sensor firing is $1
- \mathit{fn}^i$. If none of the sensed events occurred, the sensor will fire
according to its false positive probability.
}
